---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sidd

<!-- badges: start -->
<!-- badges: end -->

The sidd package contains functions to run a dynamic spatial microsimulation model that provides income and poverty projections at subnational scale. It uses a spatial microsimulation approach, to derive indicators at fine spatial resolution (e.g. districts and municipalities)  by combining socio-economic data from a household survey (referred to as the 'seed'), with   aggregated information on population characteristics (referred to as the 'benchmark') that is available for small geographical  areas from the population census and other sources. An algorithm is used to reweigh the seed and match it with the benchmark    information to derive representative small area statistics, in this case income and poverty indicators. In dynamic spatial    microsimulation approaches, the benchmark is projected forward and new weights are computed for future periods to obtain trends in income distribution under different scenarios.

## Installation

You can install the development version of sidd from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("michielvandijk/sidd")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sidd)
## basic example code
```

